Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-03 paper/galsize_paper.tex
Revised section 5.3.1

\newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}

@@

%The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering. While our results suggest that our profile co-evolution model is giving the correct qualitative picture, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} are too strong relative to SDSS. This likely indicates that the central/satellite size differences depicted in Figure \ref{fig:} are too strong, and that the correlation strength in the real Universe is intermediate, rather than maximal. Our publicly available code that reproduces our results already contains the machinery to implement continuously variable levels of $\rhalf-\rspeak$ correlation strength, but for present purposes we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.

%In addition to varying the $\rhalf-\rspeak$ correlation strength, there are other factors that should be included in any proper likelihood analysis of galaxy size models. In particular, since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. For fixed scaling relations $\langle\rhalf^{\rm cens}\vert\mhalo\rangle$ and $\langle\rhalf^{\rm sats}\vert\mhalo\rangle,$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. Our results based on the catalog that includes orphan subhalos (Figure \ref{fig:strippingorphans}, dotted curves) give an explicit demonstration of the impact of $F_{\rm sat}(\mstar)$ on the clustering signal.

%On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy sizes does not leave a pure and unique signature on $\rhalf-$clustering ratios. However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models. For this problem, the path forward is clear. Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{moster_etal13,behroozi13_smhm,lehmann_etal15}. Based on our results, we advocate that empirical models for $\langle\mstar\vert\mhalo\rangle$ be supplemented with additional model ingredients for $\langle\rhalf\vert\mstar\rangle,$ and that the parameters of composite model are jointly constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering. Careful attention will need to be paid to the orphan subhalo population, which is well-known to have a significant impact on small-scale clustering \citep{guo_white13,campbell_etal17}.

@@

%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.

>>>>

\newcommand{\mean}[2]{\langle{#1}\vert{#2}\rangle}
\newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}

@@

The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering. While our results suggest that satellite evolution {\em prior} to infall drives the correct relative size of centrals vs. satellites, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} only roughly agree with SDSS. For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.

Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering. For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations. An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction.

On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy size does not leave a pure and unique signature on $\rhalf-$clustering ratios. However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}. Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}. Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mstar},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.

@@

{\color{blue} Include new plot of clustering ratios without orphans.}
%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected. Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes. See \S\ref{subsec:satellite_discussion} for further discussion.
